\bf Estimating the number of clusters using cross-validation

### 2019-06-29 JCGS-R3/cvclust.tex
rearrange figures

\begin{figure}[H]
\centering
\includegraphics[width=5.5in, height=3.3in]{main_code/demo/bench/setting1/Facet.pdf}
\caption{Setting 1 performance as correlation increases, faceted by estimation
    method. For each estimate method, the subplot shows the proportion of
    replicates in which estimated number of clusters agrees with the truth
    versus the correlation between dimensions,~$\rho$. Gabriel
    cross-validation performance degrades under moderate correlation, but
    the correlation-corrected version performs well across all values of
    $\rho$.}
\label{fig:setting1}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=5.5in, height=3.3in]{main_code/demo/bench/setting2/Facet.pdf}
\caption{Setting 2 performance as the number of noise dimensions increases,
    faceted by estimation method. For each estimate method, the subplot shows the proportion of
    replicates in which estimated number of clusters agrees with the truth
    versus the number of noise dimensions,~$r$. Both variants of Gabriel
    cross-validation perform reasonably under all settings of~$r$, though
    not as well as some of the other methods.}
\label{fig:setting2}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=5.5in, height=3.3in]{main_code/demo/bench/setting3/Facet.pdf}
\caption{Setting 3 performance as the number of dimensions increases,
    faceted by estimation method. For each estimate method, the subplot shows the proportion of
    replicates in which estimated number of clusters agrees with the truth
    versus the number of noise dimensions,~$r$. Both variants of Gabriel
    cross-validation perform with perfect accuracy in the replicates
    with $r \geq 30$ dimensions.}

@@

\begin{figure}[H]
\centering
\includegraphics[width=5.5in, height=3.3in]{main_code/demo/bench/setting4/Facet.pdf}
\caption{Setting 4 performance as the variance heterogeneity increases,
    faceted by estimation method. For each estimate method, the subplot shows the proportion of
    replicates in which estimated number of clusters agrees with the truth
    versus the variance heterogeneity parameter,  $R$. Both variants of Gabriel
    cross-validation perform with near-perfect accuracy for all values of~$R$.}
\label{fig:setting4}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=5.5in, height=3.3in]{main_code/demo/bench/setting5/Facet.pdf}
\caption{Setting 5 performance as the tail heaviness increases,
    faceted by estimation method. For each estimate method, the subplot shows the proportion of
    replicates in which estimated number of clusters agrees with the truth
    versus the $t$~distributed noise degrees of freedom,~$\nu$, plotted
    backwards so that $\nu$ decreases from $11$ to $2$ going from left to
    right. Both variants of Gabriel cross-validation are robust to moderate
    tail heaviness, with slower performance degradation than most of the other
    estimation methods as the tail heaviness increases.}
\label{fig:setting5}
\end{figure}

@@

\begin{table}
\centering
\captionsetup{justification=centering}
\caption{\label{tab:benchmark} Number of clusters selected on benchmark datasets}
\begin{tabular}{lccc}
\toprule                  
         & \multicolumn{3}{c}{Dataset} \\
\cmidrule(l){2-4}
Method   & Congress Voting & Breast Cancer & Brain Tumours \\
\midrule                    
Gabriel  & $2$             & $3$           & $5$  \\    
Gabriel (corr.~correct) & $2$ & $2$           & $5$  \\  
Wold     & $2$             & $3$           & $4$  \\
Gap      & $8$             & $10$          & $10$ \\   
BIC      & $2$         & $5$           & $2$  \\   
CH       & $2$             & $2$           & $2$  \\
Hartigan & $3$             & $3$           & $4$  \\
Jump     & $10$            & $9$           & $1$  \\   
PS       & $2$  & $2$           & $1$  \\
Stab.    & $2$  & $2$           & $7$  \\ 
Slope	 & $2$  & $4$           & $2$ \\
\midrule 
Ground Truth & $2$         & $2$ or $3$    & $5$  \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{figure}[H]
\centering
\includegraphics[width=5.5in, height=2.75in]{main_code/demo/bench/setting1/Facet.pdf}
\caption{Setting 1 performance as correlation increases, faceted by estimation
    method. For each estimate method, the subplot shows the proportion of
    replicates in which estimated number of clusters agrees with the truth
    versus the correlation between dimensions,~$\rho$. Gabriel
    cross-validation performance degrades under moderate correlation, but
    the correlation-corrected version performs well across all values of
    $\rho$.}
\label{fig:setting1}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=5.5in, height=2.75in]{main_code/demo/bench/setting2/Facet.pdf}
\caption{Setting 2 performance as the number of noise dimensions increases,
    faceted by estimation method. For each estimate method, the subplot shows the proportion of
    replicates in which estimated number of clusters agrees with the truth
    versus the number of noise dimensions,~$r$. Both variants of Gabriel
    cross-validation perform reasonably under all settings of~$r$, though
    not as well as some of the other methods.}
\label{fig:setting2}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=5.5in, height=2.75in]{main_code/demo/bench/setting3/Facet.pdf}
\caption{Setting 3 performance as the number of dimensions increases,
    faceted by estimation method. For each estimate method, the subplot shows the proportion of
    replicates in which estimated number of clusters agrees with the truth
    versus the number of noise dimensions,~$r$. Both variants of Gabriel
    cross-validation perform with perfect accuracy in the replicates
    with $r \geq 30$ dimensions.}

@@

\begin{figure}[H]
\centering
\includegraphics[width=5.5in, height=2.75in]{main_code/demo/bench/setting4/Facet.pdf}
\caption{Setting 4 performance as the variance heterogeneity increases,
    faceted by estimation method. For each estimate method, the subplot shows the proportion of
    replicates in which estimated number of clusters agrees with the truth
    versus the variance heterogeneity parameter,  $R$. Both variants of Gabriel
    cross-validation perform with near-perfect accuracy for all values of~$R$.}
\label{fig:setting4}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=5.5in, height=2.75in]{main_code/demo/bench/setting5/Facet.pdf}
\caption{Setting 5 performance as the tail heaviness increases,
    faceted by estimation method. For each estimate method, the subplot shows the proportion of
    replicates in which estimated number of clusters agrees with the truth
    versus the $t$~distributed noise degrees of freedom,~$\nu$, plotted
    backwards so that $\nu$ decreases from $11$ to $2$ going from left to
    right. Both variants of Gabriel cross-validation are robust to moderate
    tail heaviness, with slower performance degradation than most of the other
    estimation methods as the tail heaviness increases.}
\label{fig:setting5}
\end{figure}

@@

\begin{table}
\centering
\captionsetup{justification=centering}
\caption{\label{tab:benchmark} Number of clusters selected on benchmark datasets}
    {\footnotesize
\begin{tabular}{lccc}
\toprule                  
         & \multicolumn{3}{c}{Dataset} \\
\cmidrule(l){2-4}
Method   & Congress Voting & Breast Cancer & Brain Tumours \\
\midrule                    
Gabriel  & $2$             & $3$           & $5$  \\    
Gabriel (corr.~correct) & $2$ & $2$           & $5$  \\  
Wold     & $2$             & $3$           & $4$  \\
Gap      & $8$             & $10$          & $10$ \\   
BIC      & $2$         & $5$           & $2$  \\   
CH       & $2$             & $2$           & $2$  \\
Hartigan & $3$             & $3$           & $4$  \\
Jump     & $10$            & $9$           & $1$  \\   
PS       & $2$  & $2$           & $1$  \\
Stab.    & $2$  & $2$           & $7$  \\ 
Slope	 & $2$  & $4$           & $2$ \\
\midrule 
Ground Truth & $2$         & $2$ or $3$    & $5$  \\
\bottomrule
\end{tabular}
    }
\end{table}
